19Q2

### 2019-09-04 19Q2.Rmd
work on CRISPR fusions and protein changes

```{r merge_crispr_fus, eval=FALSE}
fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
crispr_fus$Drug <- "CRISPR"
crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
crispr_fus$G2P_Drug_FusionPair <- "No"
crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
crispr_fus$Database <- "CRISPR"

saveRDS(crispr_fus, "./data_munging/rds/crispr_fusions.rds")
```

@@

saveRDS(crispr_prot, "./data_munging/rds/crispr_protein_changes.rds")
```

```{r, eval = FALSE}
crispr_fus <- readRDS("./data_munging/rds/crispr_fusions.rds")
crispr_prot <- readRDS("./data_munging/rds/crispr_protein_changes.rds")
```

>>>>

```{r merge_crispr_fus, eval=FALSE}
fusions_filt <- unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease"))
crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all = TRUE)
crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
crispr_fus$Drug <- "CRISPR"
crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
crispr_fus$G2P_Drug_FusionPair <- "No"
crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
crispr_fus$Database <- "CRISPR"

saveRDS(crispr_fus, "./../htscreens_giant_files/crispr_fusions.rds", compress = "xz")
```

@@

saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes.rds", compress = "xz")
```

```{r, eval = FALSE}
crispr_fus <- readRDS("./../htscreens_giant_files/crispr_fusions.rds")
crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
```
